
\section{Relevant Experience}

\outerlist{
\entrybig
	{\textbf{Software Engineer}}{\small September 2022 \textendash\space Present}
	{Microsoft}{}
\innerlist{
	\entry{Lead QA Tester and Release Owner: Ensured smooth product releases by identifying and resolving critical bugs, maintaining high-quality standards.}
	\entry{Scrum Master: Organised and facilitated team meetings in an Agile environment, fostering an inclusive space for equal participation among engineers.}
 	\entry{Lead Test Tools Developer: Created a comprehensive suite of test tools using Python, ensuring product compliance with specifications.}
	\entry{Infrastructure Owner: Managed internal GitLab and Artifactory deployments serving over 1,000 engineers, maintaining secure and smooth operations.}
 	\entry{Lead Tester for Production Features: Maintained code quality and oversaw testing of production features.}
 	\entry{C-Side Security Developer: Developed security features for products enhancing overall security, I worked closly with other teams to prevent bugs.}
}

\entrybig
	{\textbf{Software Engineering Intern}}{\small June 2021 \textendash\space September 2021}
	{IBM}{}
\innerlist{
	\entry{Partiapted in the extreme blue IBM internship leading a team of four over twelve weeks to build and deploy an experiance for the IBM museum.}
	\entry{Worked closely with the museum curators to ensure I delivered an experiance that would be enjoyable for visitors and be easily maintainable for the curators.}
	\entry{Created a unique augmented reality tour system for the museum running on the IBM cloud.}
	\entry{The experiance was built using a Python Django website using custom Javascript to fasiltiate the augmented reality and a PostgreSQL database. The website had an integrated an IBM AI chatbot model using Node-RED.}
}
}